Cryptobenthic reef assemblages are more distinct across a 90 m depth gradient than 2,500 km of shallow marine habitat in the Hawaiian Archipelago

### 2024-08-27 manuscript.Rmd
beginning proc b revisions

library(tidyverse)
library(pander)
library(fs)
library(here)
library(english)
library(phyloseq) 
library(vegan)
library(ggrepel)
library(here)
library(worrms)
library(BiodiversityR)
library(ggtext)

@@

The `r nsamples(cc$crabs_untransformed)` ARMS units deployed across the Hawaiian Islands (in `r format_range(cc$crab_data$depth)` m depth) yielded a total of `r num(sum(sample_sums(cc$crabs_untransformed)),1)` adult crabs. Units contained `r num(all_summary$abundance_mean,0.1)` $\pm$ `r num(all_summary$abundance_sd,0.1)` (mean $\pm$ SD) individuals, and abundance ranged from `r format_range(all_summary$abundance_range)`. Crabs were identified to `r sum(unlist(all_summary$types_breakdown))` distinct types (`r all_summary$types_breakdown$species` species and `r all_summary$types_breakdown$morphospecies` morphospecies) in `r all_summary$taxonomy_breakdown$genera` genera and `r all_summary$taxonomy_breakdown$families` families, which accounted for ~36% of the known crab diversity reported from Hawaiian waters [@castroCatalogAnomuranBrachyuran2011]. The four most abundant species were: `r with(all_summary,top_list(top,top_n,top_units,fig="fig_crabs"))`. There were `r all_summary$singleton_count` singleton taxa (morpho/species occurring in a single unit across all sites), accounting for ~`r num(all_summary$singleton_count/ntaxa(cc$crabs_untransformed)*100,1)`% of total recovered crab species. <!--`r str_to_sentence(english(all_summary$singleton_count))` species occurred in a single unit across all sites (singletons), accounting for ~`r num(all_summary$singleton_count/ntaxa(cc$crabs_untransformed)*100,1)`% of total recovered crab species.-->

>>>>

library(tidyverse)
library(pander)
library(fs)
library(here)
library(english)
library(phyloseq) 
library(vegan)
library(ggrepel)
library(here)
library(worrms)
library(ggtext)

# can't get BiodiversityR to work on new mac, but that's ok because
# all we need is this one function, which miraculously works on its own!
source(here("lib","CAPdiscrim.R"))

@@

<!-- TODO: update number of different types to reflect family/genus/species level rather than species/morphospecies level -->
The `r nsamples(cc$crabs_untransformed)` ARMS units deployed across the Hawaiian Islands (in `r format_range(cc$crab_data$depth)` m depth) yielded a total of `r num(sum(sample_sums(cc$crabs_untransformed)),1)` adult crabs. Units contained `r num(all_summary$abundance_mean,0.1)` $\pm$ `r num(all_summary$abundance_sd,0.1)` (mean $\pm$ SD) individuals, and abundance ranged from `r format_range(all_summary$abundance_range)`. Crabs were identified to `r sum(unlist(all_summary$types_breakdown))` distinct types (`r all_summary$types_breakdown$species` species and `r all_summary$types_breakdown$morphospecies` morphospecies) in `r all_summary$taxonomy_breakdown$genera` genera and `r all_summary$taxonomy_breakdown$families` families, which accounted for ~36% of the known crab diversity reported from Hawaiian waters [@castroCatalogAnomuranBrachyuran2011]. The four most abundant species were: `r with(all_summary,top_list(top,top_n,top_units,fig="fig_crabs"))`. There were `r all_summary$singleton_count` singleton taxa (morpho/species occurring in a single unit across all sites), accounting for ~`r num(all_summary$singleton_count/ntaxa(cc$crabs_untransformed)*100,1)`% of total recovered crab species.
